Search Strategies for Functional Logic Programming

### 2012-01-18 papers/atps2012/paper.tex
added new benchmark results to atps paper

\begin{figure}[ht]
\centering
\begin{tabular}{|@{~~}l@{~~}|*{7}{@{~~}r@{~~}|}}
\hline
Program &   DFS  & IDS(+1) & IDS(*2) & eDFS & eBFS & eIDS(+1) & eIDS(*2) \\\hline
PermSort  &     \\
Last      &     \\
Half      &     \\
\hline
\end{tabular}
\caption{Benchmarks: computing all values}
\label{fig:bench-all-solutions}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{tabular}{|@{~~}l@{~~}|*{7}{@{~~}r@{~~}|}}
\hline
Program     &   DFS  & IDS(+1) & IDS(*2) & eDFS  & eBFS  & eIDS(+1) & eIDS(*2) \\\hline
PermSort    &  13.12 &  841.58 &   32.77 & 38.48 & 66.82 &    72.64 &    46.79 \\
Last        &   0.10 & >10min  &    0.26 &  0.34 &  0.18 &     6.58 &     0.38 \\
Half        &   0.67 &  561.45 &    1.62 &  1.43 &  1.22 &     1.86 &     1.71 \\
Graph       &   1.76 &   52.53 &    2.40 & 3.51  & 4.22  &     4.26 &     3.83 \\
HorseMan    &   2.64 &  639.64 &    6.63 & 3.23  & 3.29  &     3.20 &     3.17 \\
MAC         &   6.80 &  544.05 &    7.84 & 21.19 & 18.34 &    18.59 &    21.03 \\
Queens      &  24.74 &  374.64 &   33.62 & 42.71 & 43.98 &    44.01 &    42.65
\hline
\end{tabular}
\caption{Benchmarks: computing all values}
\label{fig:bench-all-solutions}
\end{figure}
